\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
slightly better gdml loop sentence description

%%%%%%%%%%%%%%%%%  Replica, division, parametrised and looped volumes
A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The class which enables the creation of 
multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
in either Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
to be repeated with varying parameters. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
future release.

>>>>

%%%%%%%%%%%%%%%%%  Replica, division, parametrised and looped volumes
A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The class which enables the creation of 
multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
in either Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML can be 
 repeated with varying parameters based on the loop index. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
future release.
